---
title: "ECONODATA.CO"
output: 
  flexdashboard::flex_dashboard:
    theme: lumen
---


```{r setup, include=FALSE}
library(flexdashboard)
```


# Intraday Data Package

row
-------------------------------------
### Exchange-traded fund (ETF)

```{r}
articles <- 2695
valueBox(articles)
```


### Individual stocks

```{r}
comments <- 6436
valueBox(comments,
          color = "warning")
```


### Stock Exchanged Index

```{r}
spam <- 108
valueBox(spam)
```


### Cryptocurrency 

```{r}
spam <- 53
valueBox(spam, 
         color = "warning")
```



### Forex  

```{r}
spam <- 10
valueBox(spam)
```


# Important specifications

**Format of data:**

* All data is in csv (comma separated value) format and zipped for fast and convenient downloading. The csv format is compatible with Excel and most major analysis packages. 
* Each line in the dataset contains the times, open, high, low, close, volume for the timeframe (except for index data which does not have a volume as this is not included in the specs for most indices). 

**The intraday bars and tick data for stocks and ETFs are aggregated from trades on the below exchanges:**

* XASE (NYSE American - AMEX)
* XNAS (NASDAQ OMX BX)
* XCIS (National Stock Exchange)
* FINRA (FINRA)
* CQS (Consolidated Quote System)
* XISX (International Securities Exchange)
* EDGA (Cboe EDGA)
* EDGX (Cboe EDGX)
* XCHI (Chicago Stock Exchange)
* XNYS (New York Stock Exchange)
* ARCX (NYSE Arca)
* XNGS (Nasdaq)
* CTS (Consolidated Tape System)
* OOTC (OTC Bulletin Board)
* XOTC (OTC Bulletin Board)
* PSGM (OTC Bulletin Board)
* PINX (OTC Bulletin Board)
* OTCB (OTC Bulletin Board)
* OTCQ (OTC Bulletin Board)
* IEXG (IEX)
* XCBO (Chicago Board Options Exchange)
* PHLX (Nasdaq PSX)
* BATY (Cboe BYX)
* BATS (Cboe BZX)
* XBOS (NASDAQ BX Options/ETF)


# Stock Exchanged Index

```{r}
library(readr)
library(DT)
INDEX <- read_csv("INDEX.csv")
INDEX<-INDEX[,2:3]

datatable(
  INDEX, extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('csv', 'excel', 'pdf')
  )
)
```


# Exchange-traded fund (ETF)

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(readr)
library(DT)
library(tidyr)
ETF <- read_delim("ETF.csv", delim = ";",escape_double = FALSE, trim_ws = TRUE)
                                    
datatable(
  ETF, extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('csv', 'excel', 'pdf')
  )
)
```







# Individual stocks

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(readr)
library(DT)
library(tidyr)
STOCK <- read_csv("STOCK.csv")
STOCK<-STOCK[,2:3]                                    
datatable(
  STOCK, extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('csv', 'excel', 'pdf')
  )
)
```

#  Crypto currency

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(readr)
library(DT)
library(tidyr)
CRYPTO <- read_csv("CRYPTO.csv")
CRYPTO<-CRYPTO[,2:3]                                    
datatable(
  CRYPTO, extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('csv', 'excel', 'pdf')
  )
)
```

#  Forex

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(readr)
library(DT)
library(tidyr)
FX <- read_csv("FX.csv")
FX<-FX[,2:3]                                    
datatable(
  FX, extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('csv', 'excel', 'pdf')
  )
)
```